Using DIT to simplify the DBF feasibility test

### 2013-07-19 dit-paper.tex

Furthermore, the authors show that in the synchronous case, it is sufficient to consider intervals of the form $[0, t_d]$, where the $t_d$ correspond to job deadlines (i.e. the increases the demand-bound function) in the interval $\left[ D_{min}, H \right]$.\\

For constrained deadline set, it is sufficient to consider intervals $[0, t_d]$ with $t_d \leq L$, where $L$ is the first busy period and is the solution to the following recursive equation $$L = \sum_{i=1}^{n} \lceil \frac{L}{T_i} \rceil C_i$$ which can be computed through fixed-point iteration $$w_0 = \sum_{i=1}^{n} C_i$$ $$w_{k+1} = \sum_{i=1}^{n} \lceil \frac{w_k}{T_i} \rceil C_i$$

Even so, this test requires to check a number of instant which is exponential in the number of tasks, making the general determination of feasibility a NP-hard problem.

\section{C-space}
When developing an application, it often happens that the platform is not known in advance, in which case the value of the $C_i$ are not known. Then, it can be useful to have a description of the possible values of the $C_i$ for which the system would be feasible.

@@

The authors of \cite{george2009characterization} give the following definition of the C-space:
\begin{definition}
For a given task system $\tau$ in which the $C_i$ are not known, the \textbf{C-space} is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_n\}$ in the C-space, $\tau$ is feasible.
\end{definition}

Thus, with a good description of the C-space, it is easy to check if a given vector of $C_i$ value (given e.g. when deploying the application on a specific platform) allows the system to be scheduled or not.

@@

A region of $\mathbb{N}^n$ can be described by a list of parametric linear equations describing bounds of the convex hull of the admissible points. In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\

For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are
$$\dbf{t} = \sum_{i=1}^{n} h_i(t) C_i \leq t \; \forall t$$
Note that for a given $t$, we have that the $h_i(t)$ are constant (w.r.t. the $C_i$). Those equations are thus effectively linear.\\

@@

While redundant equations are not a problem in theory, a short description is always preferred as it can greatly reduce computation times.\\

As was shown previously, the equations corresponding to job deadlines happening before $H$ are necessary and sufficient to test the feasibility, so only those can be considered. For constrained deadline systems, the end of the first busy period has been proven to be an acceptable upper limit for the DBF test as well, but this value depends on the $C_i$ and therefore cannot be used. In section \ref{sct:DIT}, a similar concept which does not depend on the value of $C_i$ is presented.\\

>>>>

Furthermore, it is shown in \cite{baruah1990algorithms} that in the synchronous case, it is
sufficient to consider intervals of the form $[0, t_d]$, where values of
$t_d$ correspond to job deadlines (i.e. instants at which the demand-bound
function increases) in the interval $\left[ D_{min}, H \right]$.\\

For constrained deadline task sets, it is sufficient to consider intervals $[0,
t_d]$ with $t_d \leq L$, where $L$ is the length of the first busy period and is
the solution to the following recursive equation
\[
	L = \sum_{i=1}^{n} \left\lceil \frac{L}{T_i} \right\rceil C_i
\]
which can be computed through the following fixed-point iteration
\[
	\begin{array}{rl}
		w_0 = 		& \sum\limits_{i=1}^{n} C_i \\
		w_{k+1} = 	& \sum\limits_{i=1}^{n} \left\lceil \frac{w_k}{T_i} \right\rceil
		C_i
		\\
	\end{array}
\]
Even so, this test requires to check a number of time instants in $[0,
t_d]$ which is exponential in the number of tasks, making the general
determination of feasibility an NP problem.

\section{C-space}
When developing an application, it often happens that the platform is not known
in advance, in which case the value of the $C_i$ are not known. It can be
useful in those situations to have a description of the possible values of
the $C_i$ for which the system would be feasible.

@@

A definition is given in \cite{george2009characterization} :

\begin{definition}
	For a given task system $\tau$ in which the $C_i$ are not known, the
\textbf{C-space} is a region of $n = |\tau|$ dimensions (where each dimension
denotes the range of possible values of $C_i$ for a task $\tau_i$) such that
for any vector $C = \{ C_0, \cdots, C_{n-1}\}$ in the C-space, $\tau$ is
feasible.
\end{definition}

Thus, with a good description of the C-space, it is easy to check if a given
vector of $C_i$ values (given e.g. when deploying the application on a specific platform) allows the system to be scheduled or not.

@@

A region of $\mathbb{N}^n$ can be described by a list of parametric linear
inequations describing the convex hull of the admissible points. In
other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\

For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are
\[
	\dbf{t} = \sum_{i=1}^{n} C_i \cdot h_i(t) \leq t \; \forall t
\]
Note that for a given $t$, we have that the $h_i(t)$ are constants (w.r.t. the
$C_i$). Those equations are thus effectively linear.\\

@@

While redundant constraints are not a problem in theory, a short description is
always preferred as it can greatly reduce the complexity of calculating
whether a given vector of $C_i$ values is feasible.\\

As was shown previously, the equations corresponding to job deadlines happening
before $H$ are necessary and sufficient to test the feasibility of the system
and are therefore the only ones which have to be considered. For
constrained deadline systems, the end of the first busy period has been proven
to be an acceptable upper bound for the DBF test as well, but this value depends
on the $C_i$ and therefore cannot be used. In section \ref{sct:DIT}, a similar
concept which does not depend on the value of $C_i$ is presented.\\
